### 2018-08-23 doc/paper.tex
Adding in content from `proofs.tex` in thesis.

@@

>>>>

\theoremstyle{definition}
\newtheorem{lemma}{Lemma}[section]

@@

\appendix

\section{Allowing Tessellation with Inverted Triangles}

\begin{lemma}\label{lemma:bad-triangle}
Consider three smooth curves
\(b_0, b_1, b_2\) that form a closed loop: \(b_0(1) = b_1(0)\),
\(b_1(1) = b_2(0)\) and \(b_2(1) = b_0(0)\).
Take \emph{any} smooth map \(\varphi(s, t)\) on \(\utri\) that
sends the edges to the three curves:
\begin{equation}
\varphi(r, 0) = b_0(r), \quad \varphi(1 - r, r) = b_1(r),
  \quad \varphi(0, 1 - r) = b_2(r) \quad \text{for } r \in \left[0, 1\right].
\end{equation}
Then we must have
\begin{equation}
2 \int_{\utri} \det(D\varphi) \left[F \circ \varphi\right] \, dt \, ds =
\oint_{b_0 \cup b_1 \cup b_2} H \, dy - V \, dx
\end{equation}
for antiderivatives that satisfy \(H_x = V_y = F\).

When \(\det(D\varphi) > 0\), this is just the change of variables
formula combined with Green's theorem.
\end{lemma}

\begin{proof}
Let \(x(s, t)\) and \(y(s, t)\) be the components of \(\varphi\). Define
\begin{equation}
\Delta S = H(x, y) y_s - V(x, y) x_s \quad \text{and} \quad
\Delta T = H(x, y) y_t - V(x, y) x_t.
\end{equation}
On the unit triangle \(\utri\), Green's theorem gives
\begin{equation}\label{eq:basic-greens}
\int_{\mathcal{U}} \left[\partial_s \Delta T -
  \partial_t \Delta S\right] \, dV =
\oint_{\partial \mathcal{U}} \Delta S \, ds + \Delta T \, dt.
\end{equation}
The boundary \(\partial \utri\) splits into the bottom edge \(E_0\),
hypotenuse \(E_1\) and left edge \(E_2\).

Since
\begin{equation}
E_0 = \left\{ \left[ \begin{array}{c} r \\ 0 \end{array}\right] \mid
  r \in \left[0, 1\right] \right\}
\end{equation}
we take \(\varphi(r, 0) = b_0(r)\) hence
\begin{equation}
dx = x_s \, dr, dy = y_s \, dr \Longrightarrow
H dx - V dy = \Delta S \, dr.
\end{equation}
We also have \(ds = dr\) and \(dt = 0\) due to the
parameterization, thus
\begin{equation}
\int_{E_0} \Delta S \, ds + \Delta T \, dt =
  \int_{r = 0}^{r = 1} \Delta S \, dr = \int_{b_0} H \, dx - V \, dy.
\end{equation}
We can similarly verify that
\(\int_{E_j} \Delta S \, ds + \Delta T \, dt = \int_{b_j} H \, dx - V \, dy\)
for the other two edges. Combining this with~\eqref{eq:basic-greens}
we have
\begin{equation}
\int_{\mathcal{U}} \left[\partial_s \Delta T -
  \partial_t \Delta S\right] \, dV =
\oint_{b_0 \cup b_1 \cup b_2} H \, dx - V \, dy.
\end{equation}
To complete the proof, we need
\begin{equation}
\int_{\mathcal{U}} \left[\partial_s \Delta T -
  \partial_t \Delta S\right] \, dV =
2 \int_{\mathcal{U}} \det(D\varphi) \left[F \circ \varphi\right] \, dV
\end{equation}
but one can show directly that
\begin{equation}
\partial_s \Delta T - \partial_t \Delta S =
  2 \left(x_s y_t - x_t y_s\right) F(x, y) =
  2 \det(D\varphi) \left[F \circ \varphi\right]. \tag*{\qedhere}
\end{equation}
\end{proof}
